\section{Related Works}
\begin{frame}{Indoor Localization $\sim$ Wifi-based}
	\greent{PROS}
	\begin{itemize}
		\item Popular method that uses existing WiFi infrastructures, reducing deployment cost;
		\item Converts received signal strength (RSS) to distance for triangulation;
		\item Recent works use channel state information (CSI) for centimeter-level accuracy.
	\end{itemize}
	\redt{CONS}
	\begin{itemize}
		\item Low accuracy due to multipath effects in complex indoor environments;
		\item Requires knowledge of access point (AP) locations (difficult to obtain in public spaces);
		\item Fingerprinting methods based on RSS are time-consuming;
		\item CSI-based localization achieves high accuracy but has limited smartphone support.
	\end{itemize}
\end{frame}

\begin{frame}{Indoor Localization $\sim$ Dead Reckoning}
	\greent{PROS}
	\begin{itemize}
		\item Uses inertial sensor readings for real-time location estimation of a target;
		\item No extra infrastructure required;
		\item Integration with other techniques (WiFi, UWB, vision) can improve accuracy.
	\end{itemize}
	\redt{CONS}
	\begin{itemize}
		\item It suffers from accumulated error: localization accuracy decreases over time;
		\item This leads to a long-term DR being useless.
	\end{itemize}
\end{frame}


\begin{frame}{Spatial Information-Aided Localization}

	\begin{block}{Spatial Information-Aided Localization}
		Spatial knowledge aids indoor localization without extra hardware costs.
	\end{block}
	
	\begin{itemize}
		\item \textbf{Landmark matching}: map matching method;
		\item \greent{PROS}
		      \begin{itemize}
			    	\item Simple \& high operation efficient.
		      \end{itemize}
		\item \redt{CONS}
		      \begin{itemize}
			      \item Sensitive to landmark detection completeness;
			      \item Inaccurate matching may lead to a larger localization error.
		      \end{itemize}
		\item \textbf{Methods of Fusing Spatial Information}
		\item \greent{PRO}
		      \begin{itemize}
			      \item Includes richer information than basic indoor maps.
		      \end{itemize}
		\item \redt{CON}
		      \begin{itemize}
			      \item Automated reconstruction methods are in early stages, manual methods are labor-intensive and slow.
		      \end{itemize}
	\end{itemize}
\end{frame}